### 2016-07-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Began to correct gas data for burner tests; airflow rate for hose stream tests
Added air flow rate to tables in hose stream report

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
\\~\\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} \\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lcccc}
\toprule
 &  & \multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
\\ \midrule
 & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$) \\ 
\bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
\begin{tabular}{lccccc}
\toprule
 & & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$) \\ 
\midrule
 & & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.0 $\pm0.01$    &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.1 $\pm0.02$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.5 $\pm0.3$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.3 $\pm0.2$   &   1.2 $\pm0.2$  &   1.2 $\pm0.2$   &  1.3 $\pm0.2$  \\ & 
\small{(mph)} &  (2.9 $\pm0.5$)  &  (2.8 $\pm0.5$) &  (2.7 $\pm0.5$)  & (2.9 $\pm0.5$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.0 $\pm0.2$   &   0.7 $\pm0.1$  &   0.9 $\pm0.2$   &  1.0 $\pm0.2$  \\ & 
\small{(mph)} &  (2.2 $\pm0.4$)  &  (1.6 $\pm0.3$) &  (2.1 $\pm0.4$)  & (2.2 $\pm0.4$) \\ 
\bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier

>>>>

\begin{table}
\footnotesize
\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccccccc}
\toprule
 &  &  & \multicolumn{7}{c}{\normalsize ----------------------------------- 120 gpm -----------------------------------} 
\\
 &  &  & \underline{\small Test 1} &  & \multicolumn{2}{c}{\underline{\small Test 2}} &  & \multicolumn{2}{c}{\underline{\small Test 3}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
& 		 m/s 	&	 -0.3 $\pm0.1$		& &	 0.9 $\pm0.2$ 	&	 0.9 $\pm0.2$	& &	 0.7 $\pm0.1$	&	 0.7 $\pm0.1$ \\
&	&	(mph) 	& 	(-0.7 $\pm0.1$) 	& &	(2.0 $\pm0.4$)	&	(2.1 $\pm0.4$)	& &	(1.5 $\pm0.3$)	&	(1.5 $\pm0.3$) 
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
&	 	m$^3$/s	&	 -0.6 $\pm0.1$   	& &  1.5 $\pm0.3$	&	 1.5 $\pm0.3$  	& &  1.1 $\pm0.2$   & 	 1.1 $\pm0.2$ \\
& 	&	(cfm)	& 	(-1235 $\pm222$)	& & (3082 $\pm555$) &	(3272 $\pm589$) & & (2397 $\pm432$) &	(2413 $\pm434$) 
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Narrow} \\ \textit{\small Fog} \end{tabular}} & \multirow{2}{*}{Velocity}
& 		 m/s   	&    1.1 $\pm0.2$  		& &	 1.0 $\pm0.2$	&	 1.4 $\pm0.3$  	& &   0.8 $\pm0.1$  & 	 0.8 $\pm0.1$ \\
&	&	(mph) 	&	(2.5 $\pm0.5$) 		& &	(2.1 $\pm0.4$)	&	(3.2 $\pm0.6$) 	& &  (1.7 $\pm0.3$) & 	(1.7 $\pm0.3$) 
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
&		m$^3$/s &	 2.1 $\pm0.4$   	& &  1.6 $\pm0.3$	&	 2.4 $\pm0.4$  	& &  1.3 $\pm0.2$   & 	 1.2 $\pm0.2$ \\
& 	&	(cfm)	&	(4483 $\pm807$)		& & (3335 $\pm600$) &	(4980 $\pm896$) & & (2726 $\pm491$) &	(2631 $\pm474$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Wide} \\ \textit{\small Fog} \end{tabular}} & 
\multirow{2}{*}{Velocity}
& 		 m/s   	&	 2.5 $\pm0.4$  		& &  1.3 $\pm0.2$	&	 1.4 $\pm0.2$   & &	 1.2 $\pm0.2$  	& 	 0.8 $\pm0.1$ \\
& 	& 	(mph) 	&	(5.6 $\pm1.0$) 		& & (2.8 $\pm0.5$)	&	(3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) 	& 	(1.7 $\pm0.3$) 
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
&	 	m$^3$/s	&	 4.6 $\pm0.8$   	& &  2.1 $\pm0.4$	&	 2.3 $\pm0.4$  	& &  2.0 $\pm0.4$   & 	 1.3 $\pm0.2$ \\
& 	&	(cfm)	& 	(9812 $\pm1766$)	& & (4385 $\pm789$) &	(4784 $\pm861$) & & (4183 $\pm753$) &	(2738 $\pm493$)
\\
\midrule
 &  & 	& 	\multicolumn{3}{c}{\normalsize -------- 180 gpm --------} & \multicolumn{4}{c}{} 
\\
 &  & 	&	\multicolumn{3}{c}{\underline{\small Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
& 		 m/s   	&	 1.8 $\pm0.3$		&	\multicolumn{2}{c}{ 2.0 $\pm0.4$}		& \multicolumn{4}{c}{} \\
& 	&	(mph) 	&	(3.9 $\pm0.7$) 		&	\multicolumn{2}{c}{(4.4 $\pm0.8$)}		& \multicolumn{4}{c}{} 
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
&		m$^3$/s &	 2.9 $\pm0.5$  		& 	\multicolumn{2}{c}{ 3.2 $\pm0.6$}		& \multicolumn{4}{c}{} \\
& 	&	(cfm)	&	(6130 $\pm1103$) 	&	\multicolumn{2}{c}{(6884 $\pm1239$)}	& \multicolumn{4}{c}{}
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Smooth} \\ \textit{\small Bore} \end{tabular}} &
\multirow{2}{*}{Velocity}
&		 m/s  	&	 1.8 $\pm0.3$		&	\multicolumn{2}{c}{ 2.1 $\pm0.4$}		& \multicolumn{4}{c}{} \\
&	&	(mph)	&	(4.0 $\pm0.7$)		&	\multicolumn{2}{c}{(4.8 $\pm0.9$)}		& \multicolumn{4}{c}{}
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
&		m$^3$/s &	 3.0 $\pm0.5$		& 	\multicolumn{2}{c}{ 3.5 $\pm0.6$} 		& \multicolumn{4}{c}{} \\
& 	&	(cfm)	&	(6253 $\pm1126$) 	&	\multicolumn{2}{c}{(7466 $\pm1344$)} 	& \multicolumn{4}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lccccc}
\toprule
 &	&	&	\multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   0.2 $\pm0.03$	&   0.7 $\pm0.1$	&	 0.8 $\pm0.2$  \\ 
&	&	 \small{(mph)} 	&  (0.4 $\pm0.1$)	&  (1.5 $\pm0.3$)	&	(1.9 $\pm0.3$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 0.3 $\pm0.1$	&  1.2 $\pm0.2$		&	 1.6 $\pm0.3$  	\\
& 	&	\small{(cfm)}	& 	(628 $\pm113$)	& (2584 $\pm465$) 	&	(3291 $\pm592$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&	 1.7 $\pm0.3$   	&	 1.8 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&	(3.9 $\pm0.7$) 		&	(4.0 $\pm0.7$) 	&  (3.5 $\pm0.6$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.2 $\pm0.6$   	&	 3.3 $\pm0.6$		&	 2.9 $\pm0.5$  	\\
& 	&	\small{(cfm)}	& 	(6786 $\pm1222$)	&	(6977 $\pm1256$) 	&	(6228 $\pm1121$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&	 1.8 $\pm0.3$   	&   2.1 $\pm0.4$  	&   2.2 $\pm0.4$  \\ 
& 	& 	\small{(mph)}	&	(4.1 $\pm0.7$)  	&  (4.8 $\pm0.9$) 	&  (4.9 $\pm0.9$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.4 $\pm0.6$   	&  4.0 $\pm0.7$		&	 4.1 $\pm0.7$  	\\
& 	&	\small{(cfm)}	& 	(7283 $\pm1311$)	& (8463 $\pm1523$) 	&	(8669 $\pm1561$) \\
\midrule
&	&	&	\multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
& 		 \small{m/s}   	&   -0.1 $\pm0.02$    	&   0.6 $\pm0.1$   	&	 0.5 $\pm0.1$  \\ 
&	&	 \small{(mph)} 	&  (-0.2 $\pm0.04$)  	&  (1.4 $\pm0.3$) 	&	(1.2 $\pm0.2$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 -0.2 $\pm0.03$   	&  1.2 $\pm0.2$		&	 1.0 $\pm0.2$  	\\
& 	&	\small{(cfm)}	& 	(-381 $\pm69$)		& (2469 $\pm445$) 	&	(2155 $\pm388$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
& 		\small{m/s}   	&   0.9 $\pm0.2$   		&   1.5 $\pm0.3$  	&   1.6 $\pm0.3$   \\
&	&	\small{(mph)} 	&  (2.1 $\pm0.4$)  		&  (3.4 $\pm0.6$) 	&  (3.7 $\pm0.7$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 1.8 $\pm0.3$   	&  2.9 $\pm0.5$		&	 3.1 $\pm0.6$  	\\
& 	&	\small{(cfm)}	& 	(3739 $\pm673$)		& (6046 $\pm1088$) 	&	(6479 $\pm1166$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s} 	&   2.1 $\pm0.4$   		&   2.3 $\pm0.4$  	&   2.6 $\pm0.5$  \\ 
& 	& 	\small{(mph)}	&  (4.7 $\pm0.8$)  		&  (5.2 $\pm0.9$) 	&  (5.8 $\pm1.1$)  
\\ ~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 3.9 $\pm0.7$   	&  4.3 $\pm0.8$		&	 4.8 $\pm0.9$  	\\
& 	&	\small{(cfm)}	& 	(8271 $\pm1489$)	& (9165 $\pm1650$) 	&	(10273 $\pm1849$) \\
\bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity and airflow rate [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
\begin{tabular}{lcccccc}
\toprule
&	&	&	\multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & 
\begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity} 
& 		\small{m/s}		&   -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ 
&	&	\small{(mph)}	&  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 -0.3 $\pm0.1$		&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.2 $\pm0.2$  	\\
& 	&	\small{(cfm)}	& 	(-670 $\pm121$)		&	(1864 $\pm336$)		&	(2549 $\pm459$)		& 	(2602 $\pm468$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
&		\small{m/s}   	&	 0.4 $\pm0.1$   	&	 1.1 $\pm0.2$		&	 0.9 $\pm0.2$		&	 1.1 $\pm0.2$  \\ 
&	&	\small{(mph)} 	&	(0.9 $\pm0.2$)  	&	(2.4 $\pm0.4$)		&	(1.9 $\pm0.3$)		& 	(2.4 $\pm0.4$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 0.7 $\pm0.1$   	&	 1.7 $\pm0.3$		&	 1.4 $\pm0.3$  		&	 1.8 $\pm0.3$  	\\
& 	&	\small{(cfm)}	& 	(1471 $\pm265$)		&	(3688 $\pm664$) 	&	(3034 $\pm546$)		& 	(3786 $\pm682$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
&		\small{m/s}   	&    1.0 $\pm0.2$   	&	 1.0 $\pm0.2$  		&	 1.0 $\pm0.2$   	&  	 0.9 $\pm0.2$  \\  
&	&	\small{(mph)} 	&	(2.2 $\pm0.4$)  	&	(2.1 $\pm0.4$) 		&  	(2.2 $\pm0.4$)  	& 	(2.0 $\pm0.4$) 
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 1.6 $\pm0.3$   	&	 1.6 $\pm0.3$		&	 1.6 $\pm0.3$  		&	 1.4 $\pm0.3$  	\\
& 	&	\small{(cfm)}	& 	(3369 $\pm606$)		&	(3362 $\pm605$) 	&	(3453 $\pm622$)		& 	(3051 $\pm549$)
\\ \midrule
& 	& 	&	\multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Value} & \textbf{Units} &
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & 
\begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
&		\small{m/s}   	&	 0.0 $\pm0.01$		&	 0.5 $\pm0.1$  		&	 0.7 $\pm0.1$   	&	 0.7 $\pm0.1$  \\ 
&	&	\small{(mph)} 	&	(-0.1 $\pm0.02$)	&	(1.2 $\pm0.2$)		&	(1.6 $\pm0.3$)  	&	(1.5 $\pm0.3$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 -0.1 $\pm0.01$   	&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.1 $\pm0.2$  	\\
& 	&	\small{(cfm)}	& 	(-152 $\pm27$)		&	(1804 $\pm325$) 	&	(2473 $\pm445$)		& 	(2358 $\pm425$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s}   	&	 1.3 $\pm0.2$   	&	 1.2 $\pm0.2$  		&	 1.2 $\pm0.2$   	&	 1.3 $\pm0.2$  \\ 
&	&	\small{(mph)} 	&	(2.9 $\pm0.5$)  	&	(2.8 $\pm0.5$) 		&	(2.7 $\pm0.5$)  	&	(2.9 $\pm0.5$)
\\~\\
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 2.1 $\pm0.4$   	&  	 2.0 $\pm0.4$		&	 2.0 $\pm0.4$  		& 	 2.1 $\pm0.4$ 	\\
& 	&	\small{(cfm)}	& 	(4494 $\pm809$)		& 	(4326 $\pm779$) 	&	(4214 $\pm759$)		& 	(4477 $\pm806$)
\\~\\
\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
&		\small{m/s}   	&	 1.0 $\pm0.2$   	&	 0.7 $\pm0.1$  		&	 0.9 $\pm0.2$   	&	 1.0 $\pm0.2$  \\ 
&	&	\small{(mph)} 	&	(2.2 $\pm0.4$)  	&	(1.6 $\pm0.3$) 		&	(2.1 $\pm0.4$)  	& 	(2.2 $\pm0.4$) 
\\~\\ 
&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
&	 	\small{m$^3$/s}	&	 1.7 $\pm0.3$   	&	 1.2 $\pm0.2$		&	 1.6 $\pm0.3$  		& 	 1.6 $\pm0.3$	\\
& 	&	\small{(cfm)}	& 	(3509 $\pm632$)		&	(2503 $\pm451$) 	&	(3299 $\pm594$)		& 	(3428 $\pm617$)
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier
